\documentclass[options]{article}

 \usepackage[
    top    = 2.75cm,
    bottom = 2.50cm,
    left   = 4.00cm,
    right  = 3.50cm]{geometry}

\usepackage[parfill]{parskip}

\title{The Social and Academic Benefits of Team Sports}
\author{Gatale Elijah (215004651, 15/U/13927/EVE) \thanks{supervisor: Ernest Mwebaze}}
\date{%
    Makerere University\\%
    May 19, 2017
}


\begin{document}
\begin{titlepage}
\maketitle
\end{titlepage}





\section{\textbf{ Introduction}} 
Sports have become a major business and attraction at university. The
print, radio, television, internet, and cinema media have contributed to the explosive
popularity of both professional and collegiate sports. Billions of dollars are spent on the proliferating professional and collegiate sports industry. It is not surprising, therefore, that the popularity of professional and collegiate sports has been reflected in the sports programs of colleges and university.


\subsection{\textbf{Research Background}}
Athletics and academic performance has been studied at length over the years in
the literature. Research has been conducted and no consensus has been reached regarding the impact of athletic participation on academic performance at the university level. 
  \bigbreak

As a result, the relationship between the in season and out of season school academic performance of university students in one universitywas investigated in this study , it was found that athletic participation had a positive impact on academic performance and that impact may be attributable to the difference between male and female, It was determined that there was a significant relationship that existed between academic performance, measured by GPA, and athletic participation.  \bigbreak



\subsection{\textbf{Problem Statement}}
The central issue that drives this study is the relationship between academic
performance and athletic participation. The problem facing this study, and the one that will be investigated, is that there are no major studies that concentrate on sophomores and juniors with respect to the impact that their participation in athletics has on their academic performance. The purpose of the study
will now be discussed that there are a number of different conclusions drawn from various studies regarding the impact that athletics has been reported to have on academic performance.

\subsection{\textbf{Objectives}}


\subsubsection{\textbf{Main Objective}} 
 To provide straight forward assessment of the relationship between academic performance and athletic participation




\subsubsection{\textbf{Specific Objectives}}

\begin{itemize}
  \item To collect all the data necessary to aid our research.
  \item To perform a thorough analysis on the collected data.
  \item To come up with a conclusion from the data analysis.
\end{itemize}


\subsection{\textbf{Scope}}
This research is aimed at programmers or computer science students at higher institutions of learning and those at work places.

\subsection{\textbf{Purpose of the Study}}
The purpose of this study is to determine the effects of participation in athletics on
Academic performance among high school sophomores and juniors. The discussion of the literature revealed that there is no clear consensus regarding the effect that athletic participation has on academic performance. Further, previous research has identified other problems that have been traced back to athletic performance.

\section{\textbf{Research Scope}}
The study focuses more on the university level has received far more attention than the high school level. However, those studies gave some indication about the pervasiveness of a number of problems that relate to this study.

\section{\textbf{Methodology}}
In order to address the above research questions, a quantitative investigation into
the difference in GPA was conducted between in season and out of season students
at University.





\begin{thebibliography}{10} \bibitem{latexGuide}Makarere University sports department, \emph{Makerere University(June 2016)}, Available at \texttt{https://ar.mak.ac.ug/students} \end{thebibliography}



\end{document}